FoRTE baseline

### 2018-11-20 analysis/paper/paper.Rmd
Add some notes to paper draft

# Background

```{r demo, eval = FALSE}
1 + 1
```

@@

>>>>

@@

## Site description

- Secondary successional forest -- bigtooth aspen (_Populus grandidentata_), northern red oak (_Quercus rubra_), red maple (/Acer rubrum/), paper birch (_Betula papyrifera_), eastern white pine (_Pinus strobus_)
- Average age -- 95 years (2013)
- NEP in UMBS tower is 1.58 MG C ha-1 yr-1 (0.80-1.98) (1999-2006), but with landscape variation (REF?)
- Heavily logged in late 1800s and early 1900s, disturbed by fire until 1923
- Present day composition typical of upper Great Lakes region
- Previously, the site of the FASET experiment [@gough_2013_sustained; @gough_2008_multi]

## Model description: ED2

The Ecosystem Demography Model, version 2 (ED2) [@medvigy_2009_mechanistic].

Summary of common features (can move into supplement if necessary):

- Cohort-based scaling approach
- Photosynthesis / stomatal conductance
- Allometries

In this study, we run a factorial experiment of ED2 with the following features enabled or disabled:

- Radiative transfer
  - Two-stream model
    - Same general approach as in CLM 4.5 [@clm45_note], but rather than solving for just two layers (sunlit and shaded), solve for each canopy layer.
    - Set up the two-stream equations for each layer as a linear system and solve the entire set of equations numerically
    - Similar to approaches used in other models: JULES [@mercado_2007_improving], ORCHIDEE-CAN [@naudts_2015_vertically], CLM(SPA) [@bonan_2014_modeling]
  - Multiple scatter model **TODO**
